Discriminative Sensing Based on Signal Processing

### 2017-10-20 docs/thesis/chapters/2_pca_svm_cfa/pca_svm_cfa.tex
some fixes and text for tensor-dl

Critical success factor (CSF) is a management term for an element that is necessary for an organization or project to achieve its mission. CSFs represent the principal assets or areas that must be given investments to achieve better results. CSF analysis is one challenger strategic management tool, wich can provide a robust and very practical assessment for strategic planners.

@@

Recursive feature elimination (RFE) is a feature selection method for small sample classification problems. RFE seeks to improve generalization performance by recursivelly removing the least significant features whose deletion will have the least effect on training errors, according to the higher variance measured from the features \cite{chen2007enhanced}.

We propose a critical factors analysis based on Principal Compoment Analytis (PCA) and recurive feature elimination (RFE) combined with Support Vector Machine (SVM), applied to the survey that evaluates the IT governance of brazilian public organizations, in order to identify the CSF for IT governance of the public sector according to TCU. Resusts show how PCA can make the data discriminative and that SVM is the classifier that best performs and obtains an accuracy of 91.42\% to learn and classify according to TCU's IT governance evaluation of brazilian public sector. Finally, SVM is used to highlight the more significant features identified by RFE, wich are limilar to CSFs previsously identified by a qualitative analysis of the same datased.

@@

\section{Discriminative}
\label{sec:prop_getv}

In this section we evaluate the Principal Component Analysis (Principal Component Analysis) for data visualization and identification of critical factors of the evaluated dataset. Futhermore, we propose a

@@

Principal Component Analysis – PCA, é utilizada para compressão de dados para identificação das relações entre características dos dados. Tal compressão é obtida por meio da substituição das variáveis originais por um novo conjunto de variáveis, conhecidas como Componentes Principais (CPs). As CPs são obtidas pela combinação linear das variáveis que apresentam a maior variabilidade na matriz de covariância. Assim, objetivo principal da ACP é identificar as CPs responsáveis pelas maiores variações entre os resultados. Em termos práticos eliminam-se algumas variáveis com pouca informação e determinam-se as variáveis de maior influência na formação de cada CP (Vicini, 2005).
Segundo Vicini (2005), o conjunto ortogonal de eixos não correlacionados representam as variáveis que mantém ao máximo a variabilidade do conjunto, em outras palavras, a menor perda de informação. 
Conforme Vicini (2005:29), para o processo de determinação das CPs 
“é necessário calcular matriz de variância-covariância (∑), ou na matriz de correlação (), encontrar os autovalores e autovetores e, por fim, escrever as combinações lineares, que serão as novas variáveis, denominadas de componentes principais, sendo que cada componente principal é a combinação linear de todas as variáveis originais [...] em ordem de estimação e em termos da variância total, contida nos dados iniciais”. 
Ressalta-se que não são todos as CPs a serem analisadas, mas apenas as com maior variância, alguns autores (Vicini, 2005) determinam os CPs por meio da porcentagem que representam, geralmente, mais de 70\% da informação. 
Conforme Silva et al. (2012) para a geração dos CPs, considera-se uma matriz X = (X1, X2, ..., Xp) de dimensões nxp (a Seção 4 mostra as dimensões utilizadas nesta pesquisa) originada a partir de um vetor aleatório. A matriz de variância-covariância  das amostras da matriz X é calculada por meio da seguinte expressão , onde é o operador de transposição de uma matriz. Nota-se que a matriz de variância-covariância é uma matriz quadrada e não negativa. Portanto, pode-se aplica a decomposição em autovalores, do Eigenvalue Decomposition (EVD), da matriz  resultando em um produto de três matrizes.
,
% onde  é a matriz de autovetores e  é a matriz cuja diagonal principal contém os autovalores. Para cada autovalor λi da matriz  existe um autovetor unitário e ortognal vi.
vi = 
A i-nésima coluna da matriz  é o autovetor normalizado  correspondente ao autovalor . Desta forma, define-se i-ésima componente principal (Yi) como sendo
% Yi= λ i vi
Salienta-se que a ACP é baseada na EVD já que parte dos autovalores e dos autovetores representam as componentes principais (CP). 
A Figura 1 mostra geometricamente a ACP de duas variáveis X1 e X2. A nuvem de pontos representa o diagrama de espalhamento destas duas variáveis. Conforme explicado, o primeiro passo é o cálculo da matriz de variância-covariância e em seguida se aplica a EVD. Verifica-se que a CP1, denominado CP principal (com a maior variância), é ortogonal à segunda CP (CP2 com a menor variância). Note que as duas variáveis são perpendiculares porque as variáveis obtidas pela ACP são independentes. Logo, após a aplicação da ACP, ao invés de representar os dados por meio de duas variáveis correlacionadas X1 e X2, eles podem ser representados por duas variáveis independentes Y1 e Y2. Dada a elevada correlação entre X1 e X2, verifica-se que as duas variáveis X1 e X2 podem ser aproximadas por uma única variável Y1 na Figura 1.

@@

Máquina de Vetores de Suporte (MVS), do inglês Support Vector Machine (SVM), é um método supervisionado de aprendizagem de máquina, não probabilístico, baseado na teoria de aprendizagem estatística, usado para classificação, regressão e detecção de padrões. MVS pode ser aplicado por meio de dois passos: o primeiro passo é o treinamento de um modelo a partir de um determinado conjunto de dados; o segundo consiste em estimar a classificação de dados a partir da aplicação do modelo treinado. 
Quando aplicado para classificação, MVS busca a identificação de um hiperplano que separa os dados em classes distintas, por meio de uma margem máxima entre duas classes de dados. Desta forma, um conjunto de dados é linearmente separável se for possível dividir seus dados em duas classes, por meio um hiperplano, conforme na figura a seguir.

>>>>

Critical Success Factor (CSF) is a management term for an element that is necessary for an organization or project to achieve its mission. CSFs represent the principal assets or areas that must be given investments to achieve better results. CSF analysis is one challenger strategic management tool, wich can provide a robust and very practical assessment for strategic planners.

@@

Recursive Feature Elimination (RFE) is a feature selection method for small sample classification problems. RFE seeks to improve generalization performance by recursivelly removing the least significant features whose deletion will have the least effect on training errors, according to the higher variance measured from the features \cite{chen2007enhanced}.

We propose a critical factors analysis based on Principal Compoment Analytis (PCA) and RFE combined with Support Vector Machine (SVM) \cite{hearst1998support}, applied to the survey that evaluates the IT governance of brazilian public organizations, in order to identify the CSF for IT governance of the public sector according to TCU. Resusts show how PCA can make the data discriminative and that SVM is the classifier that best performs and obtains an accuracy of 91.42\% to learn and classify according to TCU's IT governance evaluation of brazilian public sector. Finally, SVM is used to highlight the more significant features identified by RFE, wich are limilar to CSFs previsously identified by a qualitative analysis of the same datased.

@@

This section presents details of the experimental scenario and describes the dataset model used to evaluate our proposal. Subsection \ref{sec:DataCollection} describes the environment and scenario adopted in order to reproduce flood and probe attacks. Subsection \ref{sec:ModelingData} presents how network traffic can be modeled as signal superposition. Subsection \ref{sec:SynfloodFraggleandPortscan} details the traffic of synflood, fraggle and port scan attacks, and Subsection \ref{sec:DarpaDataset} discusses the use of the DARPA dataset for evaluation of the proposed approach.

\section{Discriminative...}
\label{sec:prop_getv}

In this section we evaluate the PCA for data visualization and identification of critical factors of the evaluated dataset. Futhermore, we propose a

@@

PCA is a statistical technique commonly used for dimensionality reduction. It uses an orthogonal transformation to convert a set of correlated variables into a set of linearly uncorrelated variables, where the first principal components have the largest variance. PCA is a common technique for finding patterns in data of high dimension and for highlighting its discrinative characteristics and strucutres, throught an orthogonal basis transformation into new basis, by diagonalizing the centered covariance matrix of a data set {Xk E RNlk = 1, ... ,f}, defined by C = ((Xi - (Xk))(Xi - (Xk))T). The coordinates in the Eigenvector basis are called principal components. The size of an Eigenvalue >. corresponding to an Eigenvector v of C equals the amount of variance in the direction of v. PCA is usually used for signal denoising, blind source separation, data compression, data visualization, feature extraction and dimensionality reduction, where a reduced number of features is extrated retaining as much information as possible \cite{jolliffe1986principal}.

describe PCA matematically here? acho que talvez seja melhor fazer uma descricao mais alto nível e voltar depois se sobrar tempo

descrever cmo os dados são aplicados ao pca e apresentar os resultados obtidos

A Figura 1 mostra geometricamente a ACP de duas variáveis X1 e X2. A nuvem de pontos representa o diagrama de espalhamento destas duas variáveis. Conforme explicado, o primeiro passo é o cálculo da matriz de variância-covariância e em seguida se aplica a EVD. Verifica-se que a CP1, denominado CP principal (com a maior variância), é ortogonal à segunda CP (CP2 com a menor variância). Note que as duas variáveis são perpendiculares porque as variáveis obtidas pela ACP são independentes. Logo, após a aplicação da ACP, ao invés de representar os dados por meio de duas variáveis correlacionadas X1 e X2, eles podem ser representados por duas variáveis independentes Y1 e Y2. Dada a elevada correlação entre X1 e X2, verifica-se que as duas variáveis X1 e X2 podem ser aproximadas por uma única variável Y1 na Figura 1.

@@

SVM é um método supervisionado de aprendizagem de máquina, não probabilístico, baseado na teoria de aprendizagem estatística, usado para classificação, regressão e detecção de padrões. MVS pode ser aplicado por meio de dois passos: o primeiro passo é o treinamento de um modelo a partir de um determinado conjunto de dados; o segundo consiste em estimar a classificação de dados a partir da aplicação do modelo treinado. 
Quando aplicado para classificação, MVS busca a identificação de um hiperplano que separa os dados em classes distintas, por meio de uma margem máxima entre duas classes de dados. Desta forma, um conjunto de dados é linearmente separável se for possível dividir seus dados em duas classes, por meio um hiperplano, conforme na figura a seguir.

### 2017-10-20 docs/thesis/chapters/5_tensor_dl/tensor_dl.tex
some fixes and text for tensor-dl

\chapter{Tensor-Based Discriminative Dictionary Learning}
\label{ch:tensor_dl}

Tensor-Based Discriminative Dictionary Learning for Fraud Detection

>>>>

\chapter{Tensor-based Discriminative Sensing for Fraud Detection}
\label{ch:tensor_dl}

\section{Introduction}
\label{sec:introduction}

Compressive sensing is emergent for signal processing and hás been applied to Fields such as signal restoration, image processing and classification (sparce representation classification src )

Iterative dictionary learning hás been used as a blind technique for feature extraction, improving classification without require feature selection or principal conponent analysis

Big data analytics require techniques to Deal with multidimensional data, making Sense of strucutre and relationship of many dimensios. Pca is commonly adopted for dimensionality reduction and feature extraction. Tensor hás been adopted for multidimensional data analysis and can be explored for dictionary learning

Adaptive techniques for high dimensional and high thoughput

we propose to apply the tensor deconposition for dictionary learning in order to evidentiate the discriminative sensing of a fraud detection dataset

Dictionary Learning is a signal processing technique for sparse representation of signals as basis vectors, learning the representations from training data, as dictionaries. The sparse representation in terms of such dictionaries has attracted increased interest for compressive sensing and for solving problems such as denoising, compression, image processing, data decomposition, feature extraction and classification \cite{tosic2011dictionary, zhang2010discriminative, zhu2016coupled,ravishankar2011mr}.

% There are two major approaches for dictionary learning. First is the analytic approach, in which DCT bases, wavelets, curvelets and other nonadaptive functions are used as atoms to construct the dictionaries. Second is the learning-based approaches, such as the unsupervised learning for dictionary construction [9] and the online dictionary learning [11], [10], which use machine learning methods to construct the dictionary. In the analytic approach, some pre-defined functions are used to construct the dictionary. Curvelets [24], which tracks the shape of the discontinuity set, offers efficient and near-optimal representation of smooth objects. Shearlets [25], which is obtained from dilations, action of translations and shear transformations, has nice geometric properties and mathematical properties for image representation. Bandelets [26], which specifies the geometry as a vector field, is de-signed to improve the image compression and noise reduction performance. In the learning-based approach, machine learning methods are used to construct the dictionary from the training data. The least square error is used by the method of the optimal directions (MOD) [27] to update the dictionary iteratively:
% Dictionaries are either available analytically, or can be learned from a suitable training set. While analytic dictionaries permit to capture the global structure of a signal and allow a fast implementation, learned dictionaries often perform better in applications as they are more adapted to the considered class of signals.

In some applications the data and its dictionary are multidimensional, e.g., when estimating jointly behavior of users in social networks. Computing tensor decompositions of multi-way datasets is particularly useful to extract hidden patterns and structure in multidimensional data analytics problems \cite{kolda2009tensor}. Tensor-based algorithms for dictionary learning can improve the performance for cases of multidimensional and separable data, regarding the dictionary identification rating, the required number of training samples and iterations for the optimization problem \cite{roemer2014tensor}.

% In imagery, the numerical burden for (i) learning a dictionary and for (ii) employing the dictionary for reconstruction tasks only allows to deal with relatively small image patches that only capture local image information. Separable dictionaries aims at overcoming these drawbacks by allowing a separable structure on the dictionary throughout the learning process. On the one hand, this permits larger patch-sizes for the learning phase, on the other hand, the dictionary is applied efficiently in reconstruction tasks. The crucial idea is to allow the dictionary to have a separable structure, where separable means that the dictionary D is given by the Kronecker product of two smaller dictionaries A ∈ R h×a and B ∈ R w×b
% Without loss of generality we choose square image patches with w = h = 8, which is in accordance to the patch-sizes mostly used in the literature

Multidimensional parameter estimation and learning multidimensional separable dictionaries are growing research problems. Roemer \emph{et al.} \cite{roemer2014tensor} show that the multidimensional dictionary estimation problem can be efficiently formulated in terms of tensors, and that their results outperform existing schemes by exploiting the multilinear structure of the problem.

Existing dictionary learning schemes can be applied to multidimensional analysis and obtain valuable results. However, the performance of tensor-based algorithms for recovering of a known separable dictionary outperform existing schemes when dealing with growing multidimensional datasets, as can be seen in Figures \ref{fig:fig1} and \ref{fig:fig2}, which show that the recovering rating of traditional algorithms decreases over the dataset increasing.

\begin{figure}[!htb]
     \centering 
	 \includegraphics[width=0.4\textwidth]{figures/5_20_2000_1000_100.eps}
     \caption{Matrix of 1.000 elements, 2000 sample training, 100 iterations}
     \label{fig:fig1}
\end{figure}

\begin{figure}[!htb]
     \centering 
	 \includegraphics[width=0.4\textwidth]{figures/5_20_2000_24000_100.eps}
     \caption{Matrix of 24.000 elements, 2000 sample training, 100 iterations}
     \label{fig:fig2}
\end{figure}

Figures \ref{fig:fig1} and \ref{fig:fig2} show the evaluation of tensor-based and traditional dictionary learning algorithms for dictionary reconstruction of a multidimensional and separable data. Figure \ref{fig:fig1} presents the results for dictionary reconstruction from a matrix of 1000 elements by 50 atoms, while Figures \ref{fig:fig2} presents the results from a matrix with 24000 entries by 300 atoms. It is possible to observe better reconstruction rating for tensor-based algorithms.

Imbalanced data...
Recent developments in science and technology have enabled the growth and availability of raw data to occur at an explosive rate. This has created an immense opportunity for knowledge discovery and data engineering research to play an essential role in a wide range of applications from daily civilian life to national security. However, the high availability of raw data increases the challenges related to big data analytics and to imbalanced data, which corresponds to data sets exhibiting significant imbalances of classes or rare events of some classes. The fundamental issue with the imbalanced learning problem is the ability of imbalanced data to significantly compromise the performance of most standard learning algorithms

A key challenge to use sparse coding and dictionary learning for classification is how to find proper dictionaries and coefficients that highligh discriminative structure and relationships of one dataset. Therefore, we introduce a tensor-based dictionary learning method for fraud detecton from unbalanced data. Specifically, we apply a sparse representation based classification (SRC) method through learning a tensor-based dictionary and evaluate the reconstruction error for fraud classification. In this paper, we propose a tensor-based sparse representation and dictionary learning technique to analyze mobile money transactions in order to identify frauds. We propose to use tensor-based dictionary learning for learning fraudulent and legitimante data separetelly, and apply the learned dictionaries to reconstruct a test signal and classify it as fraud or ligitimate, according to the minimum reconstruction error measured by some metrics.

%However, tensor-based algorithms face challenges to achieve reasonable processing time to handle large-scale tensor factorizations \cite{de2014distributed}, demanding efforts in order to explore distributed processing techniques for tensor-based analytics of large datasets. We propose a distributed and tensor-based approach for multidimensional dictionary learning in order to obtain better processing time for larger datasets. We focus on a distributed implementation of T-MOD \cite{roemer2014tensor} algorithm, based on a modification of Almeida and Kibangou's \cite{de2014distributed} approach to use Tucker-2 decomposition. We perform experiments to test different methods for learning dictionaries, evaluating the processing time and the reconstruction of a dictionary of multidimensional and separable data.

\section{Related Works}

Face recognition...

Fisher...

Florian...

Tem que ver outro...

\section{Data Model}

Consider a generic sparse recovery problem of the following form

\begin{equation}\label{eq:eq01}
\boldsymbol{X} = \boldsymbol{A} \cdot \boldsymbol{S} + \boldsymbol{W},
\end{equation}

where $\boldsymbol{X} \in \mathbb{C}^{M \times T}$ represents $T$ consecutive observations from $M$ features, $\boldsymbol{A} \in \mathbb{C}^{M \times N}$ is the overcomplete dictionary, $\boldsymbol{S} \in \mathbb{•}hbb{C}^{N \times T}$ represents the sparse coefficient matrix, $\boldsymbol{W} \in \mathbb{C}^{M \times T}$ is the additive noise, and $M < N < T$.

Consider a sparse recovery problem for a separable 2-D manifold, i.e., a manifold that can be written as the product of two 1-D manifolds. If we choose a separable 2-D sampling grid, we can write the 2D sparse recovery problem as

Imbalance data where zero is predominante

Data divided into learning and test, with isfraud labels with 1 or 0

\begin{equation}\label{eq:eq02}
\boldsymbol{X} = (\boldsymbol{A}^{(1)} \otimes \boldsymbol{A}^{(2)}) \cdot \boldsymbol{S} + \boldsymbol{W},
\end{equation}

where $\boldsymbol{A} = (\boldsymbol{A}^{(1)} \otimes \boldsymbol{A}^{(2)})$, $\boldsymbol{A}^{(1)} \in \mathbb{C}^{M_1 \times N_1}$, $\boldsymbol{A}^{(2)} \in \mathbb{C}^{M_2 \times N_2}$, $M = M_1 \times M_2$, and $N = N_1 \times N_2$.

The Kronecker model (\ref{eq:eq02}) can be rewritten in an equivalent tensor form. Applying the algebraic rules for unfoldings of n-mode products \cite{roemer2014tensor} we can rewrite (\ref{eq:eq02}) into a "Tucker-2" decomposition, as

\begin{equation}\label{eq:eq03}
\boldsymbol{\mathcal{X}} = \boldsymbol{\mathcal{S}} \times_1 \boldsymbol{A}^{(1)} \times_2 \boldsymbol{A}^{(2)} +  \boldsymbol{\mathcal{W}},
\end{equation}

where $\boldsymbol{\mathcal{X}} \in \mathbb{C}^{M_1 \times M_2 \times T}$, $\boldsymbol{\mathcal{S}} \in \mathbb{C}^{N_1 \times N_2 \times T}$, and $\boldsymbol{\mathcal{W}} \in \mathbb{C}^{M_1 \times M_2 \times T}$ are rearranged versions of the matrices $\boldsymbol{X}$, $\boldsymbol{S}$, and $\boldsymbol{W}$ such that $\boldsymbol{X} = [\boldsymbol{\mathcal{X}}]_{(3)}^T$, $\boldsymbol{S} = [\boldsymbol{\mathcal{S}}]_{(3)}^T$, and $\boldsymbol{W} = [\boldsymbol{\mathcal{W}}]_{(3)}^T$, respectively.

We consider a randomly generated data in order to evaluate the proposed approach, where initially $\boldsymbol{A}^{(1)}$ and $\boldsymbol{A}^{(2)}$ are gaussian distributed and randomly generated, then the dictionary $\boldsymbol{A}$ is obtained. In order to be able to evaluate the dictionary reconstruction, the sparse data $\boldsymbol{\mathcal{X}}$ is generated from the dictionary $\boldsymbol{A}$, which is used for further comparisons. We adopt 20 as the signal-to-noise ratio (snr) and 5 as the sparseness factor of the data $\boldsymbol{\mathcal{X}}$.

The dictionary estimation is evaluated by applying the proposed approach to estimate the dictionary $\boldsymbol{A}$ from the sparse data $\boldsymbol{\mathcal{X}}$, according the selected number of sample training and iterations for the optimization problem.

\section{Proposed Approach}

...

\section{Experiments}

rocauc is usually used for classification evaluation, but It os not the best option for imbalance data, and Also because It does not consider the unclassified cases, such as false negatives

Due to the inherent complex characteristics of imbalanced data sets, learning from such data requires new understandings, principles, algorithms, and tools to transform vast amounts of raw data efficiently into information and knowledge representation.

We adopt precision recall curve and compare with logistic regression based on original and pca data

Classification based on reconstruction or other value, such as similarity analysis

Evaluate what metric is more discriminative, mse, tsnr or other

\section{Conclusion}

The conclusion goes here.

The importance of the right metric for classification of imbalanced data

Tensor based analysis explores the extructure and relationship of multidimensional data and can improve the discriminative power of imbalanced data for classification

Can be used for feature extraction and used for well known algorithm,  and can be used for discriminative classification based on heuristics

Our proposal is better for imbalanced data than others techniques
